s.function for 10 postcodes

### 2024-08-15 src/problem_years.Rmd
extended correction

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

>>>>

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2001 & year <2007, NA, n))

### 2024-08-15 src/problem_years_10.Rmd
extended correction

df.long %>% 
  mutate(year = as.double(year)) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text_repel(aes(x = year, y = n, label=outlier), cex = 3)

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>% 
  ungroup() %>% 
  # The next line is different than the same for  n = 1: problem.pcs$pc
  mutate(n = ifelse(pc %in% as.character(problem.pcs) & year > 2003 & year <2007, NA, n))

>>>>

df.long %>% 
  mutate(year = as.double(year)) %>% 
  ggplot() +
  geom_line(mapping = aes(x = year, y = n, group = pc), alpha = .3, size = .2) +
  ylab("N. of websites per postcode") +
  scale_x_continuous(NULL, breaks=seq(1996, 2012, 1)) +
  scale_y_continuous(labels=scales::comma) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor.x = element_blank()) 
  #geom_text_repel(aes(x = year, y = n, label=outlier), cex = 3)

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>% 
  ungroup() %>% 
  # The next line is different than the same for  n = 1: problem.pcs$pc
  mutate(n = ifelse(pc %in% as.character(problem.pcs) & year > 2001 & year <2007, NA, n))

### 2024-08-15 src/s_la_per_firm_corrected.Rmd
extended correction

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95_av.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) > 253, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 3.75, .8, 0.1)) %>%

>>>>

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only05_av.png")

@@

  #mutate(alpha = ifelse(abs(diff_1st) > 253, .8, 0.1)) %>% 
  mutate(alpha = ifelse(abs(diff_1st) <= 3.75, .8, 0.1)) %>%

### 2024-08-15 src/s_la_per_firm_corrected_10.Rmd
extended correction

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only95_av_10.png")

@@

  mutate(alpha = ifelse(abs(diff_1st) > 194.5, .8, 0.1)) %>% 
  #mutate(alpha = ifelse(abs(diff_1st) <= 5, .8, 0.1)) %>%

>>>>

out.path <- paste0(path, "/outputs/ranks/web_per_firm", t,"_2012_only05_av_10.png")

@@

  #mutate(alpha = ifelse(abs(diff_1st) > 194.5, .8, 0.1)) %>% 
  mutate(alpha = ifelse(abs(diff_1st) <= 5, .8, 0.1)) %>%
